---
title: "Helena"
output: html_document
---

```{r r_setup, include = FALSE}
## initial settings
knitr::opts_chunk$set(
  comment = NA,
  echo = TRUE,
  error = TRUE,
  cache = FALSE,
  message = FALSE,
  dpi = 96,
  warning = FALSE
)

## width to use when printing tables etc.
options(
  width = 250,
  scipen = 100,
  max.print = 5000,
  stringsAsFactors = FALSE
)

## load radiant packages if neededi
if (!exists("r_environment")) library(radiant)
```

<style>
.table {
  width: auto;
}
ul, ol {
  padding-left: 18px;
}
pre, code, pre code {
  overflow: auto;
  white-space: pre;
  word-wrap: normal;
  background-color: #ffffff;
}
</style>

## Setup

Please complete this R-markdown document by answering the questions in `s-mobile.pdf` on Dropbox (week9/readings/). The code block below will load the data you will need. Please DO NOT change the code used to load the data. Create an HTML file with all your results and comments and push both the Rmarkdown and HTML file to GitLab when you are done. All analysis results MUST be reproducible (i.e., the TA and I must be able to recreate the HTML from the R-markdown file without changes or errors). Upload all files to GitLab.

```{r}
## Loading the data from Dropbox
s_mobile <- readr::read_rds(file.path(radiant.data::find_dropbox(), "MGTA455-2019/data/s_mobile.rds"))
```

```{r}
library(tidyverse)
library(caret)
library(gbm)
```


```{r}
train = s_mobile %>%
  filter(training == 1)
test = s_mobile %>%
  filter(training == 0)
respresentative = s_mobile %>%
  filter(representative == 1)
```

```{r fig.width = 7, fig.height = 35, dpi = 144}
visualize(
  s_mobile, 
  xvar = c(
    "churn", "changer", "changem", "revenue", "mou", "overage", 
    "roam", "conference", "months", "uniqsubs", "custcare", 
    "retcalls", "dropvce", "eqpdays", "refurb", "smartphone", 
    "highcreditr", "mcycle", "car", "travel"
  ), 
  type = "dist", 
  custom = FALSE
)
```

```{r}
cm <- function(dat, vars){
  
  cm_df <- as.data.frame(matrix(NA, ncol = 4, nrow = length(vars)))
  colnames(cm_df) <- c("var", "acc", "tpr", "auc")
  
  for (i in 1:length(vars)){
    
    var <- vars[i]
    probs <- pull(dat, !!var)
    resp <- pull(dat, "churn")
    
    pred <- ifelse(pull(dat, !!var) > 0.5, "yes", "no")
    
    acc <- sum(resp == pred)/nrow(dat)
    tpr <- sum(resp == "yes" & pred == "yes")/sum(resp == "yes")
    auc <- ModelMetrics::auc(ifelse(resp=="yes",1,0), probs)

    cm_vec <- c(var, acc, tpr, auc)
    cm_df[i,] <- cm_vec
  }
  return(cm_df)
}

```

Neural Network
```{r}
## create vector storing paremeters. 
size = seq(1,10,1)
decay = c(0.1,0.5)

## create grid search matrix
params <- expand.grid(size,decay)
value <- matrix(nrow = 20,ncol = 2)
#params$auc <- NA
colnames(params) <- c("size",'decay')

auc <- c()
accuracy <- c()
for (i in 1:nrow(params)){
 
  result <- nn(
  train, 
  rvar = "churn", 
  evar = c(
    "changer", "changem", "revenue", "mou", "overage", "roam", 
    "conference", "uniqsubs", "custcare", "retcalls", "dropvce", 
    "eqpdays", "refurb", "smartphone", "highcreditr", "mcycle", 
    "car", "travel", "region", "occupation", "months"), 
  lev = "yes", 
  size = params[i,1], 
  decay = params[i,2], 
  seed = 1234
)
  pred <- predict(result, pred_data = test)
  print(i)
  test <- store(test, pred, name = name_)
  
  auc_ <- cm(test,name_)$auc
  tpr_ <- cm(test,name_)$tpr
  value[i,1] = auc_
  value[i,2] = tpr_
  colnames(value) = c('auc','tpr')
}
  params = cbind(data.frame(params),value)

saveRDS(params, "nn_tune.rds")

```

```{r} 
nn_tune <-readRDS("nn_tune.rds")
nn_tune %>% 
  arrange(auc)
```
When size = 10 and decay = 0.1, we get the highest tpr
```{r}
nn_result <- nn(
  train, 
  rvar = "churn", 
  evar = c(
    "changer", "changem", "revenue", "mou", "overage", "roam", 
    "conference", "uniqsubs", "custcare", "retcalls", "dropvce", 
    "eqpdays", "refurb", "smartphone", "highcreditr", "mcycle", 
    "car", "travel", "region", "occupation", "months"),  
  lev = "yes", 
  size = 10, 
  decay = 0.1, 
  seed = 1234
)
nn_pred <- predict(nn_result, pred_data = test)
test <- store(test, nn_pred, name = "pred_nn")
```


```{r}
## Get columns for gbm model
train_gbm = train[c("churn", "changem", "mou", "overage", "roam", "uniqsubs", "retcalls", "dropvce", "eqpdays", "refurb", "highcreditr", "mcycle", "travel", "region", "occupation", "months")]
test_gbm = test[c("churn", "changem", "mou", "overage", "roam", "uniqsubs", "retcalls", "dropvce", "eqpdays", "refurb", "highcreditr", "mcycle", "travel", "region", "occupation", "months")]
```


```{r eval=FALSE}
# Using caret
caretGrid <- expand.grid(interaction.depth = c(2,4,6), 
                         n.trees = c(100,300),
                         shrinkage = c(0.1,0.01),
                         n.minobsinnode = c(20,40))
trainControl <- trainControl(method="cv", number=6, classProbs = TRUE, summaryFunction = twoClassSummary)

set.seed(123)
gbm_caret <- train(churn ~ ., 
              data=train_gbm, 
              distribution="bernoulli", 
              method="gbm",
              trControl=trainControl, verbose=FALSE,
              tuneGrid=caretGrid, metric = "ROC")

print(gbm_caret)
gbm_caret$results
gbm_caret$bestTune

saveRDS(gbm_caret$bestTune, "gbm_best_tune_train1.rds")

saveRDS(gbm_caret$results, "gbm_tune_train1.rds")
```

```{r}
params1 <- readRDS("gbm_tune_train1.rds")
params1 %>% 
  arrange(desc(ROC)) %>% 
  top_n(ROC, n = 10)

best_tune1 <- readRDS("gbm_best_tune_train1.rds")
best_tune1
```

```{r}
train_gbm$churn <- ifelse(train_gbm$churn  == "yes", 1, 0)
test_gbm$churn <- ifelse(test_gbm$churn  == "yes", 1, 0)

best_gbm <- gbm(formula = churn ~ . , 
                  data = train_gbm, 
                  distribution = "bernoulli", 
                  interaction.depth = best_tune1[1,2],
                  shrinkage = best_tune1[1,3],
                  n.trees = best_tune1[1,1],
                  n.minobsinnode = best_tune1[1,4])

gbm_pred <- predict(best_gbm, newdata = test_gbm, type = "response", n.trees = best_tune1[1,1])
test$"pred_gbm" <- gbm_pred
```

```{r}
cols = c('pred_logit','pred_nn','pred_gbm')
cm(test,cols)
```


## logistic final model

```{r}
s_mobile$mou_log <- log(s_mobile$mou + 1)
train_val <- s_mobile %>%
  filter(representative == 0)%>%
  mutate(cweight = ifelse(churn == 'yes', 1L, 49L))

representative <- s_mobile %>%
  filter(representative == 1)
```

```{r}
result <- logistic(
  train_val, 
  rvar = "churn", 
  evar = c(
    "changer", "changem", "revenue", "overage", "roam", "conference", 
    "months", "uniqsubs", "retcalls", "dropvce", 
    "eqpdays", "refurb",  "highcreditr", "mcycle", 
   "travel", "region", "occupation", "mou_log"
  ), 
  lev = "yes", 
  wts = "cweight", 
  check = "standardize"
)
summary(result)
pred <- predict(result, pred_data = representative)
plot(result, plots = "coef", custom = FALSE)
#print(pred, n = 10)
representative <- store(representative, pred, name = "pred_logit")
```

```{r}
mean(representative$pred_logit)
```


```{r}
coef_table  <- write.coeff(result, sort = TRUE,intercept = FALSE) %>%
  select(label,OR,p.value,importance)

coef_table

coef_table %>%
  ggplot(aes(x = fct_reorder(label, importance), y = importance))+
  geom_bar(stat = 'identity') +
  coord_flip()+
  geom_hline(yintercept = 1,linetype = 'dotted',color = 'red') +
  labs(x = 'variables')
```

eqpdays - statistically speaking, 2 standard deviations increase in eqpdays, equivalent to 
`r round(2 * sd(train_val$eqpdays), 2)` days, would increase the odds of churning by 80.6%, keeping everything else constant. This is probably because that the longer the customer owning the current handset, the more the customer would desire to change to a new handset. As it is common that instead of buying a new handset from a mobile retailer, people may go to a carrier and get a much cheaper price of the same handset with signing several years of contract with the carrier. So the probability of churning increases when a customer wants to change to a new handset.

highcreditr|yes - statistically speaking,  with sd = 0.5 for an even split between "yes" and "no", highcreditr is "yes" comparing to "no", would decrease the odds of churning by 50.5%, keeping everything else constant. This is probably because that, firstly, people with low credit scores tend to have more finacial problems. When the financial problems become serious, they may have to consider to change their phone plan to a smaller carrier with a lower price or even stop using it for good.


explore the feature "eqpdays":
```{r}
summary(train_val$eqpdays)

visualize(
  s_mobile, 
  xvar = "eqpdays", 
  type = "dist", 
  custom = FALSE
)

eqpdays_c = train_val %>%
  select(churn,eqpdays)
```

```{r}
summary(representative$eqpdays)
```


option 1:
```{r}
eqpdays_c = eqpdays_c %>%
  mutate(category1 = ifelse(eqpdays<=150,'low',ifelse(eqpdays<=500,'medium','high')))

table(eqpdays_c$churn,eqpdays_c$category1)
sum(eqpdays_c$eqpdays>500)/nrow(eqpdays_c)

```

option 2 (better):
```{r}
eqpdays_c = eqpdays_c %>%
  mutate(category2 = ifelse(eqpdays<=150,'low',ifelse(eqpdays<=700,'medium','high')))

table(eqpdays_c$churn,eqpdays_c$category2)

sum(eqpdays_c$eqpdays>700)/nrow(eqpdays_c)
```
option 3 (optimal):
```{r}
eqpdays_c = eqpdays_c %>%
  mutate(category3 = ifelse(eqpdays<=100,'low',ifelse(eqpdays<=700,'medium','high')))

table(eqpdays_c$churn,eqpdays_c$category3)

sum(eqpdays_c$eqpdays<=100)/nrow(eqpdays_c)
```
After several attempts, the "high" group has a raltively high churn rate, while "low" group has a relatively low churn rate. "Medium" group has the similar amount of people churning and staying.

design an experiment:
Among all 1 million subscribers, randomly pick 1%, i.e: 10,000 people, and allocate them to group "high", "medium" and "low", for eqpdays more than 700, between 100 and 700, and less or equal to 100. Target people in group "high", offer them a discount of 5% via 36 monthly payments including a new phone and the plan based on what the customers' choices. For people in group "medium", offer them a discount of 2% via 36 monthly payments including a new phone and the plan based on what the customers' choices

method 1:

We assume that the experiment result shows that for each person in group "high", the incentive decreases the churning probability by 0.3 percent on average. And for each person in group "medium", the incentive decreases the churning probability by 0.2 percent on average

```{r}
representative$eqpdays_churn = representative$pred_logit
high_r = representative %>%
  mutate(category = ifelse(eqpdays<=100,'low',ifelse(eqpdays<=700,'medium','high'))) %>%
  filter(category == 'high') %>%
  mutate(eqpdays_churn = eqpdays_churn*0.7)
  
medium_r = representative %>%
  mutate(category = ifelse(eqpdays<=100,'low',ifelse(eqpdays<=700,'medium','high'))) %>%
  filter(category == 'medium') %>%
  mutate(eqpdays_churn = eqpdays_churn*0.8)

low_r = representative %>%
  mutate(category = ifelse(eqpdays<=100,'low',ifelse(eqpdays<=700,'medium','high'))) %>%
  filter(category == 'low') %>%
  mutate(eqpdays_churn = pred_logit)

representative_eqpdays = rbind(high_r,medium_r,low_r)
representative_eqpdays = representative_eqpdays %>%
  mutate(eqpdays_churn = ifelse(eqpdays_churn < 0, 0, eqpdays_churn))
table(representative_eqpdays$category)
summary(representative_eqpdays$eqpdays_churn)
```
To evaluate the economic impact on 5-year profitability, we made following assumptions for customer lifetime value calculation. 

1. Cost - there are 2 main components for costs, fixed and variable. The former is mainly for infrastructure and general admin maintenance and estimated to be $8 for each customer each month. The latter is variable cost which varies with service requests and we assume a cost rate of 40%;

2. Annual Discount Rate - we assume it to be 12%, which is a reasonable assumption for a company's annual rate of return;

3. Revenue arrives at the end of each month;

4. Customers cancel their plans at midst of an month, which isn't effective til the end of the month. 

5. Initial cost, namely the cost for offering a phone at the beginning of the contract(split it to every customer for easier calculation) is 50. 

6. Revenue increase associated with the new contract(split it to every customer for easier calculation) is 5
```{r}
n <- 5 * 12

fixed_cost <- rep(8, n)
initial_variable <- 0.4

revenue <- c(rep(mean(representative_eqpdays$revenue)+5, 3*12),rep(mean(representative_eqpdays$revenue),2*12))

annual_discount_rate <- 0.12
monthly_discount_rate <- (1 + annual_discount_rate)^(1/12) - 1
annual_churn <- mean(representative_eqpdays$eqpdays_churn)
monthly_churn <- 1 - (1 - annual_churn)^(1/12)

nr_years <- 5

time <- 1:(nr_years * 12)

initial_cost = 50
profit <- revenue - revenue*initial_variable - fixed_cost
active <- (1 - monthly_churn)^(time - 1)
exp_profit <- active * profit
PV_exp_profit <- exp_profit / (1 + monthly_discount_rate)^(time)
PV_exp_profit[1] = PV_exp_profit[1] - initial_cost
CLV <- cumsum(PV_exp_profit)
```

method 2:

We assume that in group "high", every 3 customers there is 1 customer would take our offer. And in group "medium", every 8 customers there is 1 customer would take our offer. Thus, we adjusted the churn rate of these customers to 0.

```{r}
high_r = representative_eqpdays %>%
  filter(category == 'high')
number1 = round(nrow(high_r)/3)
sample_high = sample_n(high_r,number1)
sample_high = sample_high %>%
  mutate(eqpdays_churn = 0)

medium_r = representative_eqpdays %>%
  filter(category == 'medium')
number2 = round(nrow(medium_r)/8)
sample_medium = sample_n(medium_r,number2)
sample_medium = sample_medium %>%
  mutate(eqpdays_churn = 0)

representative_eqpdays = anti_join(representative_eqpdays,sample_high,by = 'customer')
representative_eqpdays = anti_join(representative_eqpdays,sample_medium,by = 'customer')

all = rbind(representative_eqpdays,sample_high,sample_medium)
```


To evaluate the economic impact on 5-year profitability, we made following assumptions for customer lifetime value calculation. (The probability we used is directly derived from the logistic regression model)

1. Cost - there are 2 main components for costs, fixed and variable. The former is mainly for infrastructure and general admin maintenance and estimated to be $8 for each customer each month. The latter is variable cost which varies with service requests and we assume a cost rate of 40%;

2. Annual Discount Rate - we assume it to be 12%, which is a reasonable assumption for a company's annual rate of return;

3. Revenue arrives at the end of each month;

4. Customers cancel their plans at midst of an month, which isn't effective til the end of the month. 

5. Initial cost, namely the cost for offering a phone at the beginning of the contract(split it to every customer for easier calculation) is 50. 

6. Revenue increase associated with the new contract(split it to every customer for easier calculation) is 5

```{r}

n <- 5 * 12

fixed_cost <- rep(8, n)
initial_variable <- 0.4

revenue <- c(rep(mean(all$revenue)+5, 3*12),rep(mean(all$revenue),2*12))

annual_discount_rate <- 0.12
monthly_discount_rate <- (1 + annual_discount_rate)^(1/12) - 1
annual_churn <- mean(all$eqpdays_churn)
monthly_churn <- 1 - (1 - annual_churn)^(1/12)

nr_years <- 5

time <- 1:(nr_years * 12)

initial_cost = 50
profit <- revenue - revenue*initial_variable - fixed_cost
active <- (1 - monthly_churn)^(time - 1)
exp_profit <- active * profit
PV_exp_profit <- exp_profit / (1 + monthly_discount_rate)^(time)
PV_exp_profit[1] = PV_exp_profit[1] - initial_cost
CLV <- cumsum(PV_exp_profit)

people = (nrow(sample_high) + nrow(sample_medium))/nrow(all)

## equivalent to raising plan fee for every customer signing the contract by
5/people
```

without changes (baseline):
```{r}
n <- 5 * 12

fixed_cost <- rep(8, n)
initial_variable <- 0.4

revenue <- rep(mean(representative_eqpdays$revenue), n)

annual_discount_rate <- 0.12
monthly_discount_rate <- (1 + annual_discount_rate)^(1/12) - 1
annual_churn <- mean(representative_eqpdays$pred_logit)
monthly_churn <- 1 - (1 - annual_churn)^(1/12)

nr_years <- 5

time <- 1:(nr_years * 12)

initial_cost = 300
profit <- revenue - revenue*initial_variable - fixed_cost
active <- (1 - monthly_churn)^(time - 1)
exp_profit <- active * profit
PV_exp_profit <- exp_profit / (1 + monthly_discount_rate)^(time)
CLV <- cumsum(PV_exp_profit)
```

