---
title: "Jasmine"
output: html_document
---
Create data

```{r}
s_mobile$mou_log <- log(s_mobile$mou +1)
train <- s_mobile %>%
  filter(representative == 0) %>%
  mutate(cweight = ifelse(churn == 'yes', 1L,49L))

representative <- s_mobile %>%
  filter(representative == 1)


```
Logistic model

```{r}
result <- logistic(
  train, 
  rvar = "churn", 
  evar = c(
    "changer", "changem", "revenue", "overage", "roam", "conference", 
    "months", "uniqsubs", "retcalls", "dropvce", 
    "eqpdays", "refurb",  "highcreditr", "mcycle", 
   "travel", "region", "occupation", "mou_log"
  ), 
  lev = "yes", 
  wts = "cweight", 
  check = "standardize"
)
summary(result)
pred <- predict(result, pred_data = representative)
plot(result, plots = "coef", custom = FALSE)
#print(pred, n = 10)
representative <- store(representative, pred, name = "pred_logit")
```

Show the result in graph.
```{r}
coef_table  <- write.coeff(result, sort = TRUE,intercept = FALSE) %>%
  select(label,OR,p.value,importance)

coef_table

coef_table %>%
  ggplot(aes(x = fct_reorder(label, importance), y = importance))+
  geom_bar(stat = 'identity') +
  coord_flip()+
  geom_hline(yintercept = 1,linetype = 'dotted',color = 'red') +
  labs(x = 'variables')

```

## Question 2

Key Driver Analysis:

1. Occupation

* Retired - statistically speaking, odds of retired customer churning decrease by 82% compared to other customers, keeping everything else constant. This is probably because senior customers tend to have less expectation on mobile service, thus they are less picky. They are also reluctant to acccept new things and they won't bother calling to leave.

* Student - statistically speaking, odds of student customer churning increase by 89% compared to other customers, keeping everything else constant. This is probably because students have relatively more choices and they have less stable financial support, which both make them more likely to churn.

* Professional - statistically speaking, odds of professional customer churning increase by 42% compared to other customers, keeping everything else constant. This is probably because prefessionals are really comfortable in accepting new changes and they have high demand in a good quality mobile service. Once their need is unsatisfied, they tend to churn and switch to other providers.


2. Region

* SW,NE,SE,NW - statistically speaking, odds of churning of customers living in southwest, northeast, southeast, and northwest Singapore decrease by about 35% compared to customers from central Singapore, keeping everything else constant. Central singapore is the main metropolitan region and central business district. Many famous landmark is located there, such as merlion park, which has made it the most expensive area in singapore. Thus, we can assume that residents in central singapore tend to have higher standard on mobile services and would more likely to switch to something better if their current need is not met.

## Question 3

Actions/offers/incentives

* Open more stores in central Singapore to increase service level, such as providing help with account, and making changing plan more flexible and easy.

* Provide customized plans specially for students and professionals to meet their needs. For students plan, include more data and less messaegs. For professionals' plan, provided more data and calls.


## Question 4

```{r}
df_region <- representative %>%
  group_by(region) %>%
  summarize(count = n(),
            Churn = sum(churn == 'yes'),
            left = count - Churn,
            per = sum(churn == 'yes') / count)
df_region
```

* Test on opening new store in CS (central singapore). 

Among the 5977 CS customers in the representative data set, 2.8% of them churned in the past 30 days. Our test would be, open a new branch in CS and wait for another month. We then check precentage of people churning among the left 5808 people. Then a hypothesis testing is done to evaluate if there is significant decrease in churning rate.

Result assumption: we assume that with opening one more store, the churn rate for CS resident would go down by 15%.

* Test on create customized planning for students and professionals

```{r}
df_occupation <- representative %>%
  group_by(occupation) %>%
  summarize(count = n(),
            Churn = sum(churn == 'yes'),
            left = count - Churn,
            per = sum(churn == 'yes') / count) %>%
  arrange(desc(per))
  

df_occupation
```

Test process would be, send promotional email to students and professionals about new customized plans, and get the number of people actually accept and switch plans. Wait another 4 months to see churn rate among them. The reason to wait 4 months is people tend to need more time to adapt to new plan and figure out whether they want to stay. Then a hypothesis testing is done to evaluate if there is significant decrease in churning rate for students and professionals respectively.

Result assumption: we assume that with marketing customized plans, the churn rate for students and professionals would go down by 15% respectively.


## Question 5

* Open new store in CS

With a new store opening in CS, customers in CS are automatically targeted.

* Promote customized plans for students and professionals.

Students and professionals are targeted respectively.

## Question 6

Calculate average churn rate based on our assumption.


```{r}
ave_churn = sum(representative$churn == 'yes') / nrow(representative)

ave_churn_cs <- (df_region$Churn[1]*0.85 + sum(df_region$Churn[2:5]))/nrow(representative)

ave_churn_occ <- (sum(df_region$Churn[1:2]) *0.85 + sum(df_region$Churn[3:5]))/nrow(representative)

ave_churn_cs
ave_churn_occ
```


As for cost, we assume variable cost rate to be 40% and fixed cost is \$8 per capita per month. A little adjustment is needed when evaluate the economics. At this stage of evaluating econoics, we assume both variable cost and fixed cost remain the same. We will then estimate the maximum we can afford in cost to allow this strategy. 

### Open new store in CS

```{r}
cs_clv <- cal_clv(ave_churn_cs,0.40)
occ_clv <- cal_clv(ave_churn_occ,0.40)

```

CLV for opening a new store in CS is `r format_nr(cs_clv, '$', dec = 2)`. CLV for promoting customized plans for students and professionals is `r format_nr(occ_clv, '$', dec = 2)` 

We then calculate the maximum cost we can afford to accept the strategy.

If we choose to open new store in CS, it is a one-time build up cost, the set-up cost we can afford is just the difference between two CLVS. It is `r format_nr(cs_clv - base_clv, '$', dec = 2)`.

If we choose to promote specialized plans.

```{r}
optimize_result <- optimize(cal_diff, interval = c(0.4, 0.5), maximum = FALSE, churn_rate = ave_churn_occ) 
max_cost_rate <- optimize_result$minimum
```

Based on our calculation, we expect an increase of `r format_nr(occ_clv - base_clv, '$')` in average CLV, based on our assumptions.  To be more specific, we can spend up to `r format_nr(max_cost_rate, perc = T)` of revenues as variable cost to allow promoting specialized plans. Any cost beyond that is not worthwhile. 





Appendix

## Question 3
 
* Usage trend

Usage trend is the direct result from customer usage, we may recommend coming up with incentives in changing customer usage to decrease churning.

1. Changer

OR of changer is about 1.03, which makes it a less important driven factor in churn rate. Besides, as revenue is a mixed and comprehensive result of many influencing factor, such as infrastrucure cost and pricing. We have no recommendation in directly change revenue trend.

2. Changem

As changem is direclty related to mou, which is monthly minutes usage. We have little interest in encouraging our cusotmers to call less, thus, we prefer to find incentives from other perspectives.



* Customer action

1. Custcare

Custcare is not statistically significant in predicting churning, we would not take it into consideration.

2. retcalls

OR of rectcalls is about 1.23, which means the more customer calls retention center, the more likely they will churn. We can come up ways in improving our service, which will result in them calling less. Action would be same as opening a new store in CS to provide customer with more accessible help.

* Quality 

dropvce

Action:

Drop voice calls are always because of poor signal strength. We can invest more in infrastructure, such as building cellular towers to eliminate the area of dead zone.

```{r}
target_dropvce <- median(representative$dropvce)
target_dropvce
representative_dropvce <- representative %>% 
  mutate(dropvce = ifelse(dropvce > target_dropvce, target_dropvce, dropvce))

pred_dropvce <- predict(logit_model, newdata = representative_dropvce, type = "response") %>% 
  adjust_prob()

ave_churn_dropvce <- mean(pred_dropvce)
ave_churn_dropvce
```

## Question 4

The effect of eliminating drop voice calls to median level can decrease overall churn rate by `r format_nr(baseline - ave_churn_dropvce , perc = T, dec = 2)`.

## Question 5

The customer we target to eliminate drop voice calls are whose average dropped calls number is larger than  `r target_dropvce`.


## Question 6

```{r}
drop_clv <- cal_clv(ave_churn_dropvce,0.40)

```

If we invest more in infrastructure, it is a one-time build up cost, the set-up cost we can afford is the difference between two CLVS. It is `r format_nr(drop_clv - base_clv, '$', dec = 2)`.
